Project assignment - Tahoe-LAFS with SHA-3 candidates

### 2010-11-15 paper/main.tex
typo caused pdf not to build

\subsection {Chosen implementations}

@@

\paragraph{JH} seems to be broken in every implementation with regard to
criteria 2. For both the optimized versions found in \ac{SUPERCOP} and the
reference implementations in the \ac{NIST} submission package, Hash("foofoo")
will not give the same result as two consecutive calls to Update("foo").
However the implementation in sphlib does fulfill this requirement. We have
also contacted the author, Thomas Pornin, which confirms this problem with the
official JH candidate and that the author has been made aware of the problem
but has not released any updated version yet.
% TODO: Fix hvordan vi referer til e-post?

>>>>

\subsection{Chosen implementations}

@@

\paragraph{JH} seems to be broken in every implementation with regard to
criteria 2. For both the optimized versions found in \ac{SUPERCOP} and the
reference implementations in the \ac{NIST} submission package, Hash("foofoo")
will not yield the same result as two consecutive calls to Update("foo").
However the implementation in sphlib does fulfill this requirement. We have
also contacted the author, Thomas Pornin, which confirms this problem with the
official JH candidate and that the author has been made aware of the problem
but has not released any updated version yet.
% TODO: Fix hvordan vi referer til e-post?
